All AMCEs

### 2023-09-07 notebook/results.qmd
Add marginal means plot

# Make a little lookup table for nicer feature labels
var_lookup <- tribble(
  ~variable,      ~variable_nice,
  "feat_org",     "Organizations",
  "feat_issue",   "Issue areas",
  "feat_transp",  "Transparency",
  "feat_acc",     "Accountability",
  "feat_funding", "Funding sources",
  "feat_govt",    "Relationship with host government"
) %>% 
  mutate(amce_var = str_replace(variable, "feat_", "amces_")) %>% 
  mutate(variable_nice = fct_inorder(variable_nice))
```

@@

>>>>

# Make a little lookup table for nicer feature labels
var_lookup <- tribble(
  ~variable,      ~variable_nice,
  "feat_org",     "Organizations",
  "feat_issue",   "Issue areas",
  "feat_transp",  "Transparency",
  "feat_acc",     "Accountability",
  "feat_funding", "Funding sources",
  "feat_govt",    "Relationship with host government"
) %>% 
  mutate(amce_var = str_replace(variable, "feat_", "amces_")) %>% 
  mutate(mm_var = str_replace(variable, "feat_", "mms_")) %>% 
  mutate(variable_nice = fct_inorder(variable_nice))
```

@@

```{r plot-mms-all, fig.width=7, fig.height=6, out.width="100%"}
mms_all <- bind_rows(
  lst(
    mms_org = rename(mms_org, value = feat_org), 
    mms_issue = rename(mms_issue, value = feat_issue), 
    mms_transp = rename(mms_transp, value = feat_transp), 
    mms_acc = rename(mms_acc, value = feat_acc), 
    mms_funding = rename(mms_funding, value = feat_funding), 
    mms_govt = rename(mms_govt, value = feat_govt)
  ),
  .id = "mm_var"
) %>%
  left_join(var_lookup, by = join_by(mm_var)) %>%
  mutate(value = factor(value, levels = unique(var_levels$levels)))

ggplot(
  mms_all,
  aes(x = avg, y = value, fill = variable_nice)
) +
  geom_vline(xintercept = 0.25, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  stat_halfeye(normalize = "groups") +
  guides(fill = "none") +
  facet_col(facets = "variable_nice", scales = "free_y", space = "free") +
  scale_x_continuous(labels = label_percent()) +
  scale_fill_manual(values = clrs$prism[1:6]) +
  labs(
    x = "Marginal means of probabilities",
    y = NULL,
    title = "Posterior marginal means"
  )
```
